Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-06 main.tex
spell check

    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
    Define $\varphi_t(x) = tx$ for $t > 1$. 
    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega) \subseteq W^{p}_{0}\Lambda^{k}(\Omega)$ 
    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
    The desired result follows. 
    % 
    % Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently msall radius. The proof is complete. 
\end{proof}

@@

\caption{Left: manifold triangulation of an anulus. Right: not a manifold triangulation.}
\label{figure:not_manifold_triang}
\end{figure}

@@

    \item 
    If $2 \leq n \leq 3$ and $\calM$ has a non-empty boundary, then we use an approach as in the proof of Lemma~\ref{lemma:boundarysimplices}: 
    we let $\calM'$ denote the doubling of the manifold and $\calT'$ be the doubling of the triangulation $\calT$. 
    Let $V \in \calT$ be a vertex. 
    If $V$ is an inner vertex of $\calT$, then $\carapace(V) \subseteq \calT \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT \subseteq \calT'$ triangulates a ball of dimension $n$, as discussed above. 
    If $V$ is a boundary vertex of $\calT$, then it is an inner vertex of $\calT'$,
    and so $\carapace_{\calT}(V) \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT'$ triangulates a ball of dimension $n$.
    We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$. 
    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
    by the topological Sch\"onfliess theorem. 
    It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.

@@

We will use the following observaton, which we state without proof, 
that controls the volume and some heights when a simplex is partitioned via barycentric subdivision.

@@

	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Minako_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
	This mapping and its inverse are piecewiselinear, and it acts as the identity along $\partial \Minako_{M-1} \setminus \partial T$.
    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.

>>>>

    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
    Define $\varphi_t(x) = tx$ for $t > 1$. 
    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega) \subseteq W^{p}_{0}\Lambda^{k}(\Omega)$ 
    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
    The desired result follows. 
    % 
    % Lastly, if $k = n$ and $u$ has average zero, then so do the $\varphi_{t}^{\ast} u$ and their mollifications with sufficiently small radius. The proof is complete. 
\end{proof}

@@

\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}
\label{figure:not_manifold_triang}
\end{figure}

@@

    \item 
    If $2 \leq n \leq 3$ and $\calM$ has a non-empty boundary, then we use an approach as in the proof of Lemma~\ref{lemma:boundarysimplices}: 
    we let $\calM'$ denote the doubling of the manifold and $\calT'$ be the doubling of the triangulation $\calT$. 
    Let $V \in \calT$ be a vertex. 
    If $V$ is an inner vertex of $\calT$, then $\carapace(V) \subseteq \calT \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT \subseteq \calT'$ triangulates a ball of dimension $n$, as discussed above. 
    If $V$ is a boundary vertex of $\calT$, then it is an inner vertex of $\calT'$,
    and so $\carapace_{\calT}(V) \subseteq \calT'$ triangulates a sphere of dimension $n-1$ and $\patch_{\calT}(V) \subseteq \calT'$ triangulates a ball of dimension $n$.
    We also know that $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a sphere of dimension $n-2$ and $\patch_{\partial\calT}(V) \subseteq \partial\calT$ triangulates a ball of dimension $n-1$. 
    The embedding of $\carapace_{\partial\calT}(V) \subseteq \partial\calT$ is homeomorphic to the standard embedding of the $(n-2)$-dimensional unit sphere into the $(n-1)$-dimensional unit sphere,
    by the topological Schoenflies theorem. 
    It follows that $\carapace_{\calT}(V)$ triangulates a topological ball of dimension $n-1$.
    Since the closed cone of $\underlying{\carapace(V)}$ is homeomorphic to the star $\underlying{\patch_{\calT}(V)}$, we conclude that $\patch_{\calT}(V)$ triangulates an $n$-dimensional ball.

@@

We will use the following observation, which we state without proof, 
that controls the volume and some heights when a simplex is partitioned via barycentric subdivision.

@@

	We introduce the deformation mapping $\Xi_{2} : \patch_{\calT}(S_M) \rightarrow \Minako_{M-1}$ of Proposition~\ref{proposition:starreflection}. 
	This mapping and its inverse are piecewise linear, and it acts as the identity along $\partial \Minako_{M-1} \setminus \partial T$.
    We extend it to a bi-Lipschitz piecewise linear mapping $\Xi_{2} : X_{M} \rightarrow X_{M-1}$ by requiring that it is the identity over $X_{M-1} \setminus A_{M-1}$.
